\documentclass[letterpaper,11pt]{article}

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%\usepackage{tgheros}
%\renewcommand{\familydefault}{\sfdefault}
%\usepackage{fullpage}
%\usepackage{shading} % mysection
%\usepackage[utf8]{inputenc}
\usepackage{color,xcolor}
\usepackage[%
    pdfstartview=FitH,%
    %%CJKbookmarks=true,%
    bookmarks=true,%
    bookmarksnumbered=true,%
    bookmarksopen=true,%
    colorlinks=true,%
    citecolor=black,%
    linkcolor=black,%
    anchorcolor=green,%
    urlcolor=black%
]{hyperref}
\usepackage{tabularx}

%\textheight=9.0in
\pagestyle{empty}
\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

\linespread{0.7}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
%\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\mysection}[1]{\vspace{5pt} {\bfseries \textsl{#1}} \\ {\color{gray} \rule[5pt]{\textwidth}{1pt}}}
\newcommand{\ressubheading}[4]{\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%\newcommand{\mysection}[1]{\vspace{5pt} {\bfseries \textsl{#1}} \\ {\color{gray} \rule[5pt]{\textwidth}{0.3pt}}}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Sean Behan}  & 289--923--7907\\
    1571 Otonabee Drive &  \href{mailto:seanwbehan@gmail.com}{seanwbehan@gmail.com} \\
    Pickering, ON L1V 6T6 & \href{https://seanbehan.io}{seanbehan.io}\\
\end{tabular*}
\\

\vspace{0.1in}

\mysection{Education}
\begin{itemize}
\item
	\ressubheading{Trent University}{Peterborough, ON}{Honors B.Sc., Computer Science}{Sep. 2016--Present}
	\begin{itemize}
		\resitem{Relevant courses: Programming for Computing/Information Systems, Software Design, Linear Algebra, Computer Forensics}
	\end{itemize}
\iffalse{} % comment
\item
	\ressubheading{Dunbarton High School}{Pickering, ON}{Graduated with Diploma}{Sep. 2012--June 2016}
\fi
\end{itemize}

\mysection{Experience}
\begin{itemize}
\item
	\ressubheading{Amberlea Church}{Pickering, ON}{Volunteer role for summer camp and breakfast club}{July 2014--Aug. 2014}
	\begin{itemize}
		\resitem{Organized and prepared activities for children}
		\resitem{Responsible for the safety of children}
	\end{itemize}
\end{itemize}

%\iffalse{} % this is a multi-line comment
\mysection{Extra Curricular}
\begin{itemize}
\item
	\ressubheading{IRC support}{}{Provides technical support on the Frenode IRC network}{March 2013--Present}
\item
	%\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
	\ressubheading{Hackathons}{ON, QC}{Attended several Hackathon events across Ontario and Quebec}{Nov. 2016--Apr. 2017}
	
\item
	\ressubheading{Cisco Spark Workshop}{Toronto, ON}{Attended workshop about the Cisco Spark API}{Nov. 2016}
	
\item
	\ressubheading{AWS Courses}{}{Completed courses on the AWS Educate platform}{June 2017}
	\begin{itemize}
		\resitem{Application Developer certification}
	\end{itemize}
\end{itemize}
	%\end{tabular*}
%\fi

\mysection{Projects}
\begin{itemize}
\item
	\ressubheading{DuckDuckGo Bot}{}{Chat Bot for the Telegram chat platform that returns search URLs}{July 2016}
	\begin{itemize}
		\resitem{Learned the Telegram API in Python}
		\resitem{Used the data parsing libraries in Python to form URLs for queries}
	\end{itemize}

\item
\ressubheading{Cubes VR}{}{Virtual reality building game for the HTC Vive}{Nov. 2016}

\item
	\ressubheading{Stock Helper Bot}{}{Chat Bot for the Cisco Spark platform that returns ticker info}{Jan. 2017}
	\begin{itemize}
		\resitem{Made in 36 hours by a team of 4}
		\resitem{Learned Node.js and the Cisco Spark API}
	\end{itemize}
\end{itemize}

\mysection{Awards}
%\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
%\vspace{-6pt} \\
%\begin{tabularx}{\textwidth}{Xl}
\begin{description}
	\item[Project Management Award:]
	Trent University's Electric City Hacks Hackathon
	\item[Certificate of Technology:] High School
\end{description}
%Project Management Award & Trent University's hackathon\\
%Certificate of Technology & High School\\
%\end{tabularx}
%\vspace{-2pt}
%\end{tabular*}

\mysection{Skills}
\begin{description}
\item[Languages:]
Python, Java, C\#, C, Bash, SQL, HTML, CSS, JavaScript, Rust, \LaTeX{}, Makefile
\item[Operating Systems:]
GNU/Linux (5 years), Windows Server, BSD
\item[Applications:]
AWS, Docker, KVM/QEMU, Git, Vim, Android Studio, MS Office
\item[Interests:]
GNU/Linux, EFF, security, machine learning, music
\item[Miscellaneous:]
Fast learner, positive attitude, strong communication, excellent troubleshooting, great at problem solving, good teams skills
\end{description}

\end{document}
